\section{Requirements specification}
In this section will there be described, that we got from our contact Dorthe Kjærgaard. She sent some documentation for her ideas, about the solution and what is required in the ideal solution. 

\subsection{General requirements}

\subsection{CRM module}

The ideal solution should have a customer relationship management (CRM) module. A CRM module is used to organize and make customer information available in a organized and structured way. The CRM module should contain informations of customers, suppliers, and business contacts, thereby the CRM module should contain more information than just direct customer informations.\\

The CRM module should be able to make some automated tasks such as reminders or automated billing features. 

\subsection{Project module}

\subsection{Booking system}

\subsection{Employee module}
The ideal solution must contain a employee module. The module will contain different kinds of information about the employees such as. Some of the information would be recruitment papers which would be papers for getting a job in the organization, papers like recruitment application, the employees CV and education papers would be relevant. \\
Another group of information about the employee will be employment details such as, the employment contract, agreement between both parties and a specific job description would be relevant. The module must also contain some general information about the company and employee relationship, such a employee handbook, a organization diagram and overall job description.

\subsection{Document module}

\subsection{Sales module}